### 2015-09-11 paper.tex
Clarify chord location

\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate average
    blade chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ at tip, root, and
    mid-span, corresponding to various tow speeds at $\lambda=3.1$.}

>>>>

\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate average
    blade chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ at blade tip, root,
    and mid-span, corresponding to various tow speeds at $\lambda=3.1$.}
